---
title: "extraInserts"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

[![Build Status](https://travis-ci.org/konradedgar/extraInserts.svg?branch=master)](https://travis-ci.org/konradedgar/extraInserts)

## Description

The purpose of this trivial package is to offer a set of convenience functions inserting various pipes and operators so those can be conveniently linked to keyboard shortcuts in RStudio.

This package was developed for fun and to conveniently transport frequently used functions across environments. 

### Available operators

| Operator      | Notes                                                         |
| ------------- | ------------------------------------------------------------- |
| **`->`**      | [Rightwards form of common assignment operator][1]            |
| **`%<>%`**    | Pipe operators offered in the excellent [magrittr][2] package |
| **`%T>%`**    | The "tee" operator from the [magrittr][2] package             |

## Installation

```{r installation, eval=FALSE, echo=TRUE}
if (!requireNamespace("devtools", quietly = TRUE))
  install.packages("devtools")
devtools::install_github('konradedgar/extraInserts')
```

[1]: https://stat.ethz.ch/R-manual/R-devel/library/base/html/assignOps.html
[2]: https://cran.r-project.org/web/packages/magrittr/vignettes/magrittr.html 
