---
title: "extraInserts"
output:
  rmarkdown::github_document:
    html_preview: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- badges: start -->

[![R-CMD-check](https://github.com/konradedgar/extraInserts/workflows/R-CMD-check/badge.svg)](https://github.com/konradedgar/extraInserts/actions)

<!-- badges: end -->

## Description

The purpose of this trivial package is to offer a set of convenience functions inserting various (pipe) operators so those can be conveniently linked to
keyboard shortcuts in [RStudio](https://www.rstudio.com/products/RStudio/).

This package was developed for fun and to conveniently transport frequently used functions across environments.

### Available operators

For every operator listed below an [RStudio add-in](https://rstudio.github.io/rstudioaddins/) is registered, allowing RStudio users to assign a [custom
shortcut](https://support.rstudio.com/hc/en-us/articles/206382178-Customizing-Keyboard-Shortcuts-in-the-RStudio-IDE) to it or to invoke it from the [command
palette](https://www.rstudio.com/blog/rstudio-1-4-a-quick-tour/#command-palette--shortcuts).

```{r, echo=FALSE}
# define operator overview table data
operator_overview <-
    tibble::tribble(
        ~operator, ~description,
        "->", "Rightwards form of the [common **assignment** operator](https://rdrr.io/r/base/assignOps.html)",
        "%in%", "Syntactic-sugar version of [**`match`**](https://rdrr.io/r/base/match.html)",
        "%>%", "[**Pipe** operator](https://magrittr.tidyverse.org/reference/pipe.html) from the [magrittr](https://magrittr.tidyverse.org/) package",
        "%<>%", "[**Assignment pipe** operator](https://magrittr.tidyverse.org/reference/compound.html) from the [magrittr](https://magrittr.tidyverse.org/) package",
        "%$%", "[**Exposition pipe** operator](https://magrittr.tidyverse.org/reference/exposition.html) from the [magrittr](https://magrittr.tidyverse.org/) package",
        "%!>%", "[**Eager pipe** operator](https://magrittr.tidyverse.org/reference/pipe-eager.html) from the [magrittr](https://magrittr.tidyverse.org/) package",
        "%T>%", "[**Tee pipe** operator](https://magrittr.tidyverse.org/reference/tee.html) from the [magrittr](https://magrittr.tidyverse.org/) package",
        "%||%", "[**NULL default** operator](https://rlang.r-lib.org/reference/op-null-default.html) from the [rlang](https://rlang.r-lib.org/) package",
        "%|%", "[**NA default** operator](https://rlang.r-lib.org/reference/op-na-default.html) from the [rlang](https://rlang.r-lib.org/) package",
    )

# print overview table
operator_overview |>
    dplyr::mutate(operator = paste0("**`", operator, "`**")) |>
    dplyr::rename_with(.cols = everything(),
                       .fn = stringr::str_to_title) |>
    gt::gt() |>
    gt::fmt_markdown(columns = everything()) |>
    gt::tab_options(column_labels.font.weight = "bold") |>
    # avoid separate HTML <style> tag for GFM
    gt::as_raw_html(inline_css = TRUE)
```

## Installation

```{r installation, eval=FALSE, echo=TRUE}
if (!requireNamespace("remotes", quietly = TRUE)) {
    install.packages("remotes")
}
remotes::install_github('konradzdeb/extraInserts')
```

