---
title: "extraInserts"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

[![Build Status](https://travis-ci.org/konradzdeb/extraInserts.svg?branch=master)](https://travis-ci.org/konradzdeb/extraInserts)

## Description

The purpose of this trivial package is to offer a set of convenience functions inserting various (pipe) operators so those can be conveniently linked to
keyboard shortcuts in [RStudio](https://www.rstudio.com/products/RStudio/).

This package was developed for fun and to conveniently transport frequently used functions across environments.

### Available operators

|  Operator  | Description                                                                                                                              |
|:----------:|:-----------------------------------------------------------------------------------------------------------------------------------------|
|  **`->`**  | Rightwards form of the [common assignment operator](https://rdrr.io/r/base/assignOps.html)                                               |
| **`%in%`** | Syntactic-sugar version of [`match`](https://rdrr.io/r/base/match.html)                                                                  |
| **`%<>%`** | The *compound assignment pipe operator* offered in the excellent [magrittr](https://magrittr.tidyverse.org/) package                     |
| **`%T>%`** | The *tee operator* from the [magrittr](https://magrittr.tidyverse.org/) package                                                          |
| **`%$%`**  | The *exposition pipe operator* from the [magrittr](https://magrittr.tidyverse.org/) package                                              |
| **`%||%`** | The [*NULL default operator*](https://rlang.r-lib.org/reference/op-null-default.html) from the [rlang](https://rlang.r-lib.org/) package |
| **`%|%`**  | The [*NA default operator*](https://rlang.r-lib.org/reference/op-na-default.html) from the [rlang](https://rlang.r-lib.org/) package     |

## Installation

```{r installation, eval=FALSE, echo=TRUE}
if (!requireNamespace("remotes", quietly = TRUE)) {
  install.packages("remotes")
}
remotes::install_github('konradzdeb/extraInserts')
```
