---
title: "extraInserts"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

[![Build Status](https://travis-ci.org/konradzdeb/extraInserts.svg?branch=master)](https://travis-ci.org/konradzdeb/extraInserts)

## Description

The purpose of this trivial package is to offer a set of convenience functions inserting various (pipe) operators so those can be conveniently linked to keyboard shortcuts in [RStudio](https://www.rstudio.com/products/RStudio/).

This package was developed for fun and to conveniently transport frequently used functions across environments. 

### Available operators

| Operator      | Description                                                                                  |
| :-----------: | :------------------------------------------------------------------------------------- |
| **`->`**      | Rightwards form of the [common assignment operator][1]                                 |
| **`%<>%`**    | The _compound assignment pipe-operator_ offered in the excellent [magrittr][2] package |
| **`%T>%`**    | The _tee operator_ from the [magrittr][2] package                                      |
| **`%$%`**     | The _exposition pipe-operator_ from the [magrittr][2] package                          |

## Installation

```{r installation, eval=FALSE, echo=TRUE}
if (!requireNamespace("remotes", quietly = TRUE)) {
  install.packages("remotes")
}
remotes::install_github('konradzdeb/extraInserts')
```

[1]: https://rdrr.io/r/base/assignOps.html
[2]: https://magrittr.tidyverse.org/
